Togglge Smell Detection in Google Chrome

### 2015-12-07 paper/paper.tex
add the benifit of our algorithm for detecting ever file or os search

\subsection{Enumerations Interface}
In Java there is a support to manage set of states through “enum” interface which is much richer when compared to languages like C, C++ (C++11 has similar support). The enum can implement interfaces and provide some flexibility in defining the toggle API (Togglz framework uses this approach) to use rather than using the constant variables directly.\\

public enum ToggleFlags
{
    FEATURE1(false),
    FEATURE2(true),
    FEATURE3(false);\\

    private boolean state;
    private ToggleFlags(boolean state) { this.state = state; }\\

    public boolean isEnabled() { return this.state; }
}\\

@@

@@

@@

\subsection{Combinatorial (Spaghetti) Toggle Smell Detection}

@@

>>>>

\subsection{Enumerations Interface}
In Java there is a support to manage set of states through “enum” interface which is much richer when compared to languages like C, C++ (C++11 has similar support). The enum can implement interfaces and provide some flexibility in defining the toggle API (Togglz framework uses this approach) to use rather than using the constant variables directly.\\
\begin{lstlisting}
public enum ToggleFlags
{
    FEATURE1(false),
    FEATURE2(true),
    FEATURE3(false);

@@

\textbf{Advantages of our approach:}

Our approach to detect the toggle smells uses the abstract syntax trees from the eclipse CDT API. This makes the present solution extensible for future enhancements to suggest or perform automated or semi-automated refactorings to eliminate the dead/stable toggle from the target system.

Our solution could also be extended to do a software repository mining to identify the potential stable and dead toggle flags used in the project. The solution could then present the list of identified dead/stable toggles and present it to the developer and upon his/her confirmation could act on the detection of dead/stable toggle smells.

This way the solution does not expect manual input from the user.

@@

\textbf{Advantages of our approach: }

Presenting a solution as an plugin within an IDE like eclipse facilitates the developers to quickly navigate to the file where the smell is found. Our solution results only the places where the nested toggle smell is observed ignoring other occurrences where the toggle method name is called. So the solutions presents more narrowed down results which saves time of the developer.

As of today we are not aware of a search filter which can customize the search results such as find two or more occurrences of the invocation of the toggle method name within same class or same method.

@@

@@

\textbf{Advantages of our solution}

Our solution has an upper hand when compared with the manual searching through os commands or IDE search options might result in a large data set to correlate, compare and come to a conclusion of potential toggle smell.

Our solution presents the toggle flag name, file path and low level details like line number which saves lot of time for the developers to identify this toggle smell.
